A Dearth of Young Stars and Planets in the Kepler Field

### 2024-06-04 paper/ms.tex
update ms

To select stars with rotation periods, we turn to previous work.  Many
investigators have derived rotation periods both specifically for KOIs
\citep{McQuillan_2013,Walkowicz_2013,Mazeh_2015,Angus_2018,David_2021},
and also for the broader set of all Kepler target stars
\citep{McQuillan_2014,Reinhold_2015,Santos_2019,Santos_2021}.  These
studies used a range of detection methods and selection functions.  We
are interested in understanding the age distribution of all Kepler
target stars irrespective of KOI status.  Out of these studies, the
only homogeneous analysis of both Kepler targets and KOIs were the
studies by \citet{Santos_2019,Santos_2021}, hereafter \citetalias{Santos_2019}
and \citetalias{Santos_2021}.  \citetalias{Santos_2019} and
\citetalias{Santos_2021} combined a wavelet analysis and
autocorrelation-based approach, and cumulatively reported rotation
periods for 55{,}232 main-sequence and subgiant FGKM stars.  They
included known KOIs and binaries in their analysis, and removed
transits and eclipses during the stellar rotation measurement process.

@@

\appendix
\section{Defining An ``Isochronally Far From The Main Sequence'' Boundary}
\label{app:linemethod}

>>>>

To select stars with rotation periods, we turn to previous work.  Many
investigators have derived rotation periods both specifically for KOIs
\citep{McQuillan_2013,Walkowicz_2013,Mazeh_2015,Angus_2018,David_2021},
and also for the broader set of all Kepler target stars
\citep{McQuillan_2014,Reinhold_2015,Santos_2019,Santos_2021,Reinhold2023}.
These studies used a range of detection methods and selection
functions.  We are interested in understanding the age distribution of
all Kepler target stars irrespective of KOI status.  Out of these
studies, the most homogeneous and precise analyses of both Kepler
targets and KOIs appear to be those by
\citet{Santos_2019,Santos_2021}, hereafter \citetalias{Santos_2019}
and \citetalias{Santos_2021}.  
For a discussion of the work by \citet{Reinhold2023}, please see
Appendix~\ref{app:reinhold23}.
\citetalias{Santos_2019} and
\citetalias{Santos_2021} combined a wavelet analysis and
autocorrelation-based approach, and cumulatively reported rotation
periods for 55{,}232 main-sequence and subgiant FGKM stars.  They
included known KOIs and binaries in their analysis, and removed
transits and eclipses during the stellar rotation measurement process.

@@

\appendix

\section{Regarding The Preferred Rotation Period Catalog}
\label{app:reinhold23}

While we opted for our default stellar rotation periods to be those
reported by \citetalias{Santos_2019} and \citetalias{Santos_2021},
the more recent analysis by \citet{Reinhold2023} bears comment.  \citet{Reinhold2023} used a
similar selection function as \citetauthor{Santos_2021}, and
considered a novel period measurement approach based on gradients of
power spectra (GPS).
Their method likely provides greater completeness, due
to its greater sensitivity to signals that are only weakly periodic.
However,
 comparing 
overlapping stars from
\citet{McQuillan_2014}, \citetalias{Santos_2019},
\citetalias{Santos_2021}, and \citet{Reinhold2023} suggested that for
stellar signals that are strongly periodic, 
the GPS method is likely a factor of a few times less precise than 
the more traditional approaches (ACF, Lomb-Scargle, or wavelet
analysis).

{\bf TODO: finish writing!}
{\bf TODO: finish writing!}
{\bf TODO: finish writing!}

%TODO: how many "new rotatoin periods" would this reinhold catalog
%yield?
%TODO: maybe you should just report ages for them!!

\section{Defining An ``Isochronally Far From The Main Sequence'' Boundary}
\label{app:linemethod}
